\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-06-16 draft.tex
reverse uncertainty and pfs sections

I show in the \hyperlink{psf}{Appendix} that choosing the following political weighting function aligns the political objective function used in the current model with the PFS framework:
		    \begin{equation}
		      \ga(e) = 1 + \frac{e}{a\pi_X(\tau)} .
		      \label{eq:gh}
		    \end{equation}
Although using the $\ga$-weighted government welfare function is a reduced-form approach in the sense that legislative dynamics are not fully modeled, a benefit is that it does not require returns to lobbying effort to be constant. The more flexible form of the weighting function also removes the equilibrium indeterminacies and inability to speak to distributional questions that are implied by the linear form and its transferable utility (Dixit, Grossman and Helpman 1997).

\subsection{The Role of Political Uncertainty}
\label{sec:uncertainty}
In this model, if there were no political uncertainty, there would be no lobbying in equilibrium. Thus, if nothing else, adding the realism of political uncertainty allows for positive lobbying on the equilibrium path. If we examine more closely the assumption that there is significant uncertainty surrounding the legislative lobbying process, additional insights come to light. It is most clear in the case of mean-zero uncertainty, so I will assume this throughout this section unless otherwise noted.

@@

\begin{figure}
\begin{center}
\includegraphics[height=3in, width=4in]{lobby_br.jpg}
\end{center}
\caption{Lobby's Optimal Expenditure Function (Low and Intermediate Uncertainty)\label{fig:lobby_br}}
\end{figure}

@@

>>>>

\subsection{The Role of Political Uncertainty}
\label{sec:uncertainty}
Adding political uncertainty allows for positive lobbying on the equilibrium path, but this is not the only additional insight. These are most clear in the case of mean-zero uncertainty, so I will assume this throughout this section unless otherwise noted.

@@

\begin{figure}
\begin{center}
\includegraphics[height=2.5in, width=3in]{lobby_br.jpg}
\end{center}
\caption{Lobby's Optimal Expenditure Function (Low and Intermediate Uncertainty)\label{fig:lobby_br}}
\end{figure}

@@

I show in the \hyperlink{pfs}{Appendix} that choosing the following political weighting function aligns the political objective function used in the current model with the PFS framework:
		    \begin{equation}
		      \ga(e) = 1 + \frac{e}{a\pi_X(\tau)} .
		      \label{eq:gh}
		    \end{equation}
Although using the $\ga$-weighted government welfare function is a reduced-form approach in the sense that legislative dynamics are not fully modeled, a benefit is that it does not require returns to lobbying effort to be constant. The more flexible form of the weighting function also removes the equilibrium indeterminacies and inability to speak to distributional questions that are implied by the linear form and its transferable utility (Dixit, Grossman and Helpman 1997).
